Developmental trajectories of word recognition: a priming study in bilinguals

### 2023-10-18 manuscript/manuscript.qmd
Render manuscript to arxiv-pdf and add Oxford data

targets::tar_load(c(participants, stimuli, vocabulary,
					attrition_trials, attrition_participants,
					attrition_trials_vtarget, attrition_participants_vtarget,
					attrition_trials_vnone, attrition_participants_vnone,
					attrition_trials_noeach, attrition_participants_noeach,
					bvq_data, gaze_aoi, 
					data_time_related, data_time_cognate,
					data_time_related_vtarget, data_time_cognate_vtarget,
					data_time_related_vnone, data_time_cognate_vnone,
					data_time_related_noeach, data_time_cognate_noeach))

targets::tar_load(
	c(model_fits_related,
	  model_fits_cognate,
	  model_fits_related_vtarget,
	  model_fits_cognate_vtarget,
	  model_fits_related_vnone,
	  model_fits_cognate_vnone,
	  model_fits_related_noeach,
	  model_fits_cognate_noeach,
	  model_loo_related,
	  model_loo_cognate,
	  model_loo_related_vtarget,
	  model_loo_cognate_vtarget,
	  model_loo_related_vnone,
	  model_loo_cognate_vnone,
	  model_loo_related_noeach,
	  model_loo_cognate_noeach
	))

@@

attrition_trials_vtarget <- left_join(attrition_trials_vtarget, 
									  select(participants, id, age_group, lp, filename))

@@

attrition_trials_vnone <- left_join(attrition_trials_vnone, 
									select(participants, id, age_group, lp, filename))

@@

attrition_trials_noeach <- left_join(attrition_trials_noeach, 
									 select(participants, id, age_group, lp, filename))

@@

```{r}
#| label: tbl-participants-lp
#| tbl-cap: "Description of language profile of test participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
participants |> 
	filter(is_valid_participant) |> 
	select(id, age_group, age, lp,
		   doe_catalan, doe_spanish, test_language) |> 
	mutate(id = paste0(id, " (", age_group, ")")) |>
	add_count(lp, 
			  name = "n_lp") |> 
	add_count(age_group, 
			  name = "n_age_group") |> 
	pivot_longer(starts_with("doe_"),
				 names_to = "language",
				 values_to = "doe") |>
	add_count(age_group,
			  test_language,
			  name = "n_age_test") |> 
	mutate(language = str_to_sentence(str_remove_all(language, "doe_")),
		   age_group = paste0(age_group, " (N = ", n_age_group, ")"),
		   test_language = paste0("Tested in ", test_language, 
		   					   " (N = ", n_age_test, ")"),
		   lp = factor(lp, levels = rev(unique(lp))))  |> 
	summarise(across(c(doe, age), lst(mean, sd)),
			  .by = c(age_group, lp, test_language, language)) |> 
	pivot_wider(id_cols = c(age_group, test_language),
				names_from = c(language, lp),
				values_from = c(matches("doe"), age_mean, age_sd),
				names_repair = janitor::make_clean_names) |> 
	relocate(age_group, test_language,
			 matches("monolingual"),
			 matches("bilingual")) |> 
	select(-c(age_mean_spanish_monolingual,
			  age_mean_spanish_bilingual,
			  age_sd_spanish_monolingual,
			  age_sd_spanish_bilingual)) |> 
	arrange(age_group, test_language) |> 
	gt(rowname_col = "test_language", 
	   groupname_col = "age_group", 
	   row_group.sep = ": ") |> 
	tab_spanner(md("Monolingual (*N* = 162)"), matches("monolingual")) |> 
	tab_spanner(md("Bilingual (*N* = 133)"), matches("bilingual")) |>
	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
	fmt_number(matches("age"), decimals = 1) |> 
	cols_merge_uncert(col_val = age_mean_catalan_monolingual, 
					  col_uncert = age_sd_catalan_monolingual) |> 
	cols_merge_uncert(col_val = age_mean_catalan_bilingual, 
					  col_uncert = age_sd_catalan_bilingual) |> 
	cols_merge_uncert(col_val = doe_mean_catalan_monolingual,
					  col_uncert = doe_sd_catalan_monolingual) |> 
	cols_merge_uncert(col_val = doe_mean_catalan_bilingual,
					  col_uncert = doe_sd_catalan_bilingual) |> 
	cols_merge_uncert(col_val = doe_mean_spanish_monolingual, 
					  col_uncert = doe_sd_spanish_monolingual) |> 
	cols_merge_uncert(col_val = doe_mean_spanish_bilingual, 
					  col_uncert = doe_sd_spanish_bilingual) |> 
	cols_label(age_mean_catalan_monolingual = "Age (months)",
			   age_mean_catalan_bilingual = "Age (months)",
			   doe_mean_catalan_monolingual = "Catalan (%)",
			   doe_mean_catalan_bilingual = "Catalan (%)",
			   doe_mean_spanish_monolingual = "Spanish (%)",
			   doe_mean_spanish_bilingual = "Spanish (%)") |> 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners())) |> 
	tab_style(cell_text(size = "medium"),
			  list(cells_body(),
			  	 cells_stub()))
```

## Vocabulary size

@@

```{r tbl-vocabulary}
#| label: tbl-vocabulary
#| tbl-cap: "Vocabulary sizes. Total: proportion of words in both languages marked as *Understands*. L1: proportion of words in the dominant language marked as *Understands*. L2: proportion of words in the non-cominant language marked as *Understands*. Conceptual: proportion of translation equivalents for which at least one of the words has ben marked as *Understands*. TE: proportion of translation equivalents for which *both* words have been marked as *Understands*."
vocabulary |> 
	left_join(select(participants, filename, id, age_group, lp),
			  by = join_by(filename)) |> 
	summarise(across(matches("prop"), 
					 tibble::lst(mean, sd)),
			  .by = c(age_group, lp)) |>
	arrange(age_group, lp) |> 
	gt(groupname_col = "age_group",
	   rowname_col = "lp") |> 
	cols_hide(lp) |> 
	tab_spanner("Total ", matches("total")) |> 
	tab_spanner("L1", matches("l1")) |> 
	tab_spanner("L2", matches("l2")) |> 
	tab_spanner("Conceptual", matches("concept")) |> 
	tab_spanner("TE", matches("te_")) |> 
	tab_spanner("Vocabulary size (%)", matches("prop_")) |> 
	cols_merge_uncert(total_prop_mean, total_prop_sd) |> 
	cols_merge_uncert(l1_prop_mean, l1_prop_sd) |> 
	cols_merge_uncert(l2_prop_mean, l2_prop_sd) |> 
	cols_merge_uncert(concept_prop_mean, concept_prop_sd) |> 
	cols_merge_uncert(te_prop_mean, te_prop_sd) |> 
	fmt_number(is.numeric, 
			   drop_trailing_zeros = FALSE) |> 
	cols_label(total_prop_mean = "Mean (SD)",
			   l1_prop_mean = "Mean (SD)",
			   l2_prop_mean = "Mean (SD)",
			   concept_prop_mean = "Mean (SD)",
			   te_prop_mean = "Mean (SD)") |> 
	tab_stub_indent(rows = everything(),
					indent = 2) |> 
	tab_style(cell_text(align = "left"),
			  cells_stub())
```

@@

For each word, we created a picture with a typical referent.

```{r tbl-stimuli}
#| label: tbl-stimuli
#| tbl-cap: "Summary of stimuli properties by trial type."
stimuli |> 
	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
					 tibble::lst(mean, sd, min, max)),
			  .by = c(test_language, trial_type)) |> 
	select(-matches("familiarity_se"), -matches("prime"),
		   -c(is_animate_target_sd,
		      is_animate_target_min,
		      is_animate_target_max)) |> 
	gt(groupname_col = "test_language",
	   rowname_col = "list") |> 
	tab_spanner("Prevalence (%)", matches("familiarity")) |> 
	tab_spanner("Frequency (Zipf)", matches("freq")) |>
	tab_spanner("Animacy (%)", matches("animate")) |> 
	tab_spanner("Duration (s)", matches("duration")) |> 
	fmt_number(is.numeric) |> 
	cols_merge_range(familiarity_target_min, familiarity_target_max) |> 
	cols_merge_range(freq_target_min, freq_target_max) |> 
	cols_merge_range(duration_min, duration_max) |>
	cols_merge_uncert(freq_target_mean, freq_target_sd) |> 
	cols_merge_uncert(familiarity_target_mean, familiarity_target_sd) |> 
	cols_merge_uncert(duration_mean, duration_sd) |> 
	cols_label(trial_type = "",
			   familiarity_target_mean = "Mean ± SD",
			   # familiarity_target_sd = "SD",
			   familiarity_target_min = "Range",
			   freq_target_mean = "Mean ± SD",
			   # freq_target_sd = "SD",
			   freq_target_min = "Range",
			   is_animate_target_mean = "",
			   duration_mean = "Mean ± SD",
			   # duration_sd = "SD",
			   duration_min = "Range") 
```

@@

@@

```{r tbl-attrition-trials}
#| label: tbl-attrition-trials
#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
attrition_trials |> 
	filter(id %in% attrition_participants$id[attrition_participants$is_valid_participant]) |> 
	left_join(select(participants, filename, id, age_group),
			  by = join_by(filename, id, age_group)) |> 
	summarise(n_valid = sum(is_valid_trial),
			  n_total = n(),
			  .by = c(id, age_group, trial_type)) |> 
	summarise(across(n_valid, lst(sum, mean, sd),
					 .names = "{.fn}"),
			  n_total = sum(n_total),
			  .by = c(age_group, trial_type)) |> 
	mutate(n_excluded = n_total-sum) |> 
	select(-c(n_total)) |> 
	pivot_wider(names_from = trial_type,
				values_from = c(sum:sd, n_excluded),
				names_repair = janitor::make_clean_names) |> 
	rename_with(\(x) gsub("non_cognate", 
						  "noncognate",
						  x)) |> 
	arrange(age_group) |> 
	relocate(age_group,
			 matches("_cognate"),
			 matches("noncognate")) |> 
	gt(rowname_col = "age_group") |> 
	grand_summary_rows(columns = matches("mean_"),
					   fns = lst(Mean ~ mean(.)),
					   fmt = ~fmt_number(.)) |>
	grand_summary_rows(columns = matches("sum_"),
					   fns = lst(Sum ~ sum(.)),
					   fmt = ~fmt_integer(.)) |>
	cols_merge(c(sum_cognate, n_excluded_cognate), 
			   pattern = "{1} ({2})") |> 
	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
			   pattern = "{1} ({2})") |> 
	cols_merge(c(sum_unrelated, n_excluded_unrelated),
			   pattern = "{1} ({2})") |> 
	cols_merge_uncert(mean_cognate, sd_cognate) |> 
	cols_merge_uncert(mean_noncognate, sd_noncognate) |> 
	cols_merge_uncert(mean_unrelated, sd_unrelated) |> 
	tab_spanner("Cognate trials", ends_with("_cognate")) |>
	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
	tab_spanner("Related trials", matches("cognate")) |>
	fmt_number(matches("mean|sd")) |> 
	fmt_integer(matches("sum"), sep_mark = ",") |> 
	cols_label(sum_cognate = "N",
			   sum_noncognate = "N",
			   sum_unrelated = "N",
			   mean_cognate = "Mean",
			   mean_noncognate = "Mean",
			   mean_unrelated = "Mean")
```

@@

A model including the *Relatedness* $\times$ *Group* interaction showed the best of-of-sample predictive performance, although the model including only *Relatedness* performed equivalently ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_1}}$ = `r round(model_loo_related[2, 1], 3)`, *SE* = `r round(model_loo_related[2, 2], 3)`). Both models showed substantially better predictive performance than the model including only *Group* ($\text{ELPD}_{\mathcal{M_0}} - \text{ELPD}_{\mathcal{M_2}}$ = `r round(model_loo_related[3, 1], 3)`, *SE* = `r round(model_loo_related[3, 2], 3)`). This indicates that including the *Relatedness* predictor improved the predictive performance of the model significantly, that including its interaction with *Group* slightly increased the performance of the model, and that the main effect of *Group* by itself barely changed the predictive performance of the model.

```{r fig-related}
#| label: fig-related
#| fig-height: 6
#| fig-width: 8
#| fig-cap: "Marginal posterior predictions of the GAMMs. (A) Mean posterior probability of target looking across the time course of the trial. Black lines and intervals indicate the psoterior mean and 95% credible intervals. Points indicate the mean probability of target looking across participants. (B) Difference in posterior probability of target looking between *related* and *unrelated* trials. The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
epreds <- expand_grid(condition = levels(data_time_related$condition),
					  timebin = seq(0, 17, length.out = 100),
					  age = mean(data_time_related$age),
					  lp = levels(data_time_related$lp),
					  .nsamples = 1) |>
	add_epred_draws(model_fits_related[[4]],
					ndraws = NULL,
					re_formula = NA, 
					value = ".value") |> 
	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))

@@

>>>>

targets::tar_load(
	c(participants,
	  participants_oxf,
	  stimuli,
	  stimuli_oxf,
	  vocabulary,
	  vocabulary_oxf,
	  attrition_trials, 
	  attrition_participants,
	  attrition_trials_vtarget,
	  attrition_participants_vtarget,
	  attrition_trials_vnone, 
	  attrition_participants_vnone,
	  attrition_trials_noeach,
	  attrition_participants_noeach,
	  attrition_trials_vnoeach,
	  attrition_participants_vnoeach,
	  attrition_trials_oxf, 
	  attrition_participants_oxf,
	  attrition_trials_vtarget_oxf,
	  attrition_participants_vtarget_oxf,
	  attrition_trials_vnone_oxf, 
	  attrition_participants_vnone_oxf,
	  attrition_trials_noeach_oxf,
	  attrition_participants_noeach_oxf,
	  attrition_trials_vnoeach_oxf,
	  attrition_participants_vnoeach_oxf,
	  bvq_data, 
	  gaze_aoi, 
	  looking_times,
	  data_time_related, 
	  data_time_cognate,
	  data_time_related_vtarget,
	  data_time_cognate_vtarget,
	  data_time_related_vnone,
	  data_time_cognate_vnone,
	  data_time_related_noeach, 
	  data_time_cognate_noeach,
	  data_time_related_vnoeach,
	  data_time_cognate_vnoeach,
	  data_time_related_oxf, 
	  data_time_cognate_oxf,
	  data_time_related_vtarget_oxf,
	  data_time_cognate_vtarget_oxf,
	  data_time_related_vnone_oxf,
	  data_time_cognate_vnone_oxf,
	  data_time_related_noeach_oxf, 
	  data_time_cognate_noeach_oxf,
	  data_time_related_vnoeach_oxf,
	  data_time_cognate_vnoeach_oxf
	))

targets::tar_load(
	c(model_fits_related,
	  model_fits_cognate,
	  model_fits_related_vtarget,
	  model_fits_cognate_vtarget,
	  model_fits_related_vnone,
	  model_fits_cognate_vnone,
	  model_fits_related_noeach,
	  model_fits_cognate_noeach,
	  model_fits_related_vnoeach,
	  model_fits_cognate_vnoeach
	  # model_loo_related,
	  # model_loo_cognate,
	  # model_loo_related_vtarget,
	  # model_loo_cognate_vtarget,
	  # model_loo_related_vnone,
	  # model_loo_cognate_vnone,
	  # model_loo_related_noeach,
	  # model_loo_cognate_noeach,
	  # model_loo_related_vnoeach,
	  # model_loo_cognate_vnoeach
	))

@@

attrition_trials_vtarget <- attrition_trials_vtarget |> 
	left_join(select(participants, id, age_group, lp, filename))

@@

attrition_trials_vnone <- attrition_trials_vnone |> 
	left_join(select(participants, id, age_group, lp, filename))

@@

attrition_trials_noeach <- attrition_trials_noeach |> 
	left_join(select(participants, id, age_group, lp, filename))

attrition_participants_vnoeach <- attrition_participants_vnoeach |> 
	left_join(select(participants, id, age_group, lp, filename))

attrition_trials_vnoeach <- attrition_trials_vnoeach |> 
	left_join(select(participants, id, age_group, lp, filename))

@@

```{r}
#| label: tbl-participants-lp
#| tbl-cap: "Description of language profile of test participants. Data are summarised for each age group, and for monolinguals and bilinguals separately."
participants_oxf |> 
	left_join(attrition_participants_oxf,
			  by = join_by(id)) |> 
	mutate(lp = "Monolingual (English)",
		   id = as.character(id)) |> 
	bind_rows(mutate(participants, id = as.character(id))) |> 
	filter(is_valid_participant) |> 
	select(id, age_group, age, lp, test_language) |> 
	add_count(lp, 
			  name = "n_lp") |> 
	add_count(age_group, 
			  name = "n_age_group") |> 
	add_count(age_group,
			  test_language,
			  name = "n_age_test") |> 
	mutate(lp = factor(lp, levels = rev(unique(lp))))  |> 
	summarise(across(c(age), lst(mean, sd)),
			  n = n(),
			  .by = c(age_group, lp, test_language)) |> 
	pivot_wider(id_cols = c(test_language, lp),
				names_from = c(age_group),
				values_from = c(matches("doe"), age_mean, age_sd, n),
				names_repair = janitor::make_clean_names) |> 
	relocate(lp, test_language,
			 matches("21"),
			 matches("25"),
			 matches("30"),
	) |> 
	arrange(lp, test_language) |> 
	gt(rowname_col = "test_language", 
	   groupname_col = "lp", 
	   row_group.sep = ": ") |> 
	tab_spanner(md("21 months"), matches("21")) |> 
	tab_spanner(md("25 months"), matches("25")) |>
	tab_spanner(md("30 months"), matches("30")) |> 
	fmt_number(matches("age"), decimals = 1) |>
	cols_merge(c(age_mean_21_months, age_sd_21_months),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(age_mean_25_months, age_sd_25_months),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(age_mean_30_months, age_sd_30_months),
			   pattern = "{1} ({2})") |> 
	cols_label(n_21_months = md("*N*"),
			   n_25_months = md("*N*"),
			   n_30_months = md("*N*"),
			   age_mean_21_months = "Age (months)",
			   age_mean_25_months = "Age (months)",
			   age_mean_30_months = "Age (months)") |> 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners())) |> 
	tab_style(cell_text(size = "medium"),
			  list(cells_body(),
			  	 cells_stub()))
```

### Vocabulary size

@@

```{r tbl-vocabulary}
#| label: tbl-vocabulary
#| tbl-cap: "Summary of participant vocabulary sizes. vocabulary sizes are expressed as percentage points, and summarised as the mean (*M*) and the standard deviation (*SD*). Total: proportion of words in both languages marked as *Understands*. L1: proportion of words in the dominant language marked as *Understands*. L2: proportion of words in the non-cominant language marked as *Understands*. Conceptual: proportion of translation equivalents for which at least one of the words has ben marked as *Understands*. TE: proportion of translation equivalents for which *both* words have been marked as *Understands*."
#| eval: false
vocabulary |> 
	left_join(select(participants, filename, id, age_group, lp),
			  by = join_by(filename)) |> 
	summarise(across(matches("prop"), 
					 tibble::lst(mean, sd)),
			  .by = c(age_group, lp)) |>
	arrange(age_group, lp) |> 
	gt(groupname_col = "age_group",
	   rowname_col = "lp") |> 
	cols_hide(lp) |> 
	tab_spanner("Vocabulary size ", matches("prop")) |> 
	cols_merge(c(total_prop_mean, total_prop_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(l1_prop_mean, l1_prop_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(l2_prop_mean, l2_prop_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(concept_prop_mean, concept_prop_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(te_prop_mean, te_prop_sd),
			   pattern = "{1} ({2})") |> 
	fmt_number(is.numeric,
			   decimals = 1,
			   scale_by = 100,
			   drop_trailing_zeros = FALSE) |>
	cols_label(total_prop_mean = "Total",
			   l1_prop_mean = "L1",
			   l2_prop_mean = "L2",
			   concept_prop_mean = "Concept",
			   te_prop_mean = "TE") |> 
	tab_stub_indent(rows = everything(),
					indent = 2) |> 
	tab_style(cell_text(align = "left"),
			  cells_stub())
```

@@

For each word, we created a picture with a typical referent. To avoid competition between target and distractor pictures, semantically related target-distractor pairs were perceptually distinct [@floccia2020translation; @arias-trejo2010].

```{r tbl-stimuli}
#| label: tbl-stimuli
#| tbl-cap: "Summary of stimuli properties by trial type."
stimuli |> 
	summarise(across(c(matches("familiarity_|freq_|animate_"), duration),
					 tibble::lst(mean, sd, min, max)),
			  .by = c(test_language, trial_type)) |> 
	select(-matches("familiarity_se"), -matches("prime"),
		   -c(is_animate_target_sd,
		      is_animate_target_min,
		      is_animate_target_max),
		   -matches("min"), -matches("max")) |> 
	gt(groupname_col = "test_language",
	   rowname_col = "list") |> 
	fmt_number(is.numeric,
			   decimals = 1) |> 
	fmt_number(matches("familiarity|animate"),
			   scale_by = 100,
			   decimals = 1) |> 
	cols_merge(c(freq_target_mean, freq_target_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(familiarity_target_mean, familiarity_target_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(duration_mean, duration_sd),
			   pattern = "{1} ({2})") |> 
	cols_label(trial_type = "",
			   familiarity_target_mean = "Prevalence (%)",
			   freq_target_mean = "Frequency",
			   is_animate_target_mean = "Animacy (%)",
			   duration_mean = "Duration (s)") 
```

@@

We know present the results under four different trial-level inclusion criteria In Analysis 1, the child is required to understand the prime *and* the target words, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase. In Analysis 2, the child is required to understand the target word, on top of having to fixate both target and distractor  for at last 50 ms each during the target-distractor phase. In Analysis 3, the child is not required to understand any word, but is still required to fixate both target and distractor for at last 50 ms each during the target-distractor phase. In Analysis 4, the child is not required to understand any word, nor to fixate at both target and distractor.

For reference:

* [@floccia2020translation] requires participants to know prime and target, but not to look at target *and* distractor (looking at at least one of them is enough).

The fact that in some time course analyses participants seem to be looking predominantly towards one of the objects (despite the target and distractor pictures having been presented less than 300 ms before) is a common finding in previous studies using preferential looking procedures [e.g., @floccia2020translation].

```{r tbl-multi-trials}
tibble::lst(data_time_related,
			data_time_related_oxf,
			data_time_related_vtarget,
			data_time_related_vtarget_oxf,
			data_time_related_vnone,
			data_time_related_vnone_oxf,
			data_time_related_noeach,
			data_time_related_noeach_oxf,
			data_time_related_vnoeach,
			data_time_related_vnoeach_oxf) |> 
	bind_rows(.id = "analysis") |>
	mutate(analysis_lab = case_when(
		analysis=="data_time_related" ~ "Analysis 1",
		grepl("_vtarget", analysis) ~ "Analysis 2",
		grepl("_vnone", analysis) ~ "Analysis 3",
		grepl("_noeach", analysis) ~ "Analysis 4",
		grepl("_vnoeach", analysis) ~ "Analysis 5",
		.default = "Analysis 1"
	),
	lp = case_when(grepl("_oxf", analysis) ~ "Monolingual (Oxford)", 
				   lp=="Bilingual" ~ "Bilingual (Barcelona)",
				   .default = "Monolingual (Barcelona)"),
	lp = factor(lp, 
				levels = c("Monolingual (Oxford)",
						   "Monolingual (Barcelona)",
						   "Bilingual (Barcelona)")),
	condition = factor(condition, levels = c("Related", "Unrelated"))) |> 
	distinct(analysis, analysis_lab, lp, condition, .ntrials) |> 
	summarise(.ntrials = sum(.ntrials),
			  .by = c(lp, analysis_lab, condition)) |> 
	pivot_wider(names_from = c(lp, condition),
				values_from = .ntrials,
				names_repair = janitor::make_clean_names) |> 
	relocate(matches("oxford"), matches("barcelona")) |> 
	gt(rowname_col = "analysis_lab") |> 
	tab_spanner("Monolingual", matches("monolingual")) |> 
	tab_spanner("Bilingual", matches("bilingual")) |> 
	tab_spanner("Barcelona", matches("barcelona")) |> 
	tab_spanner("Oxford", matches("oxford")) |>

	cols_label(monolingual_oxford_related = "Related",
			   monolingual_oxford_unrelated = "Unrelated",
			   monolingual_barcelona_related = "Related",
			   monolingual_barcelona_unrelated = "Unrelated",
			   bilingual_barcelona_related = "Related",
			   bilingual_barcelona_unrelated = "Unrelated")

```{r fig-related-summary}
#| label: fig-related-summary
#| fig-height: 6.5
#| fig-width: 8
#| fig-cap: "Marginal posterior predictions of the GAMMs. (A) Mean posterior probability of target looking across the time course of the trial. Black lines and intervals indicate the psoterior mean and 95% credible intervals. Points indicate the mean probability of target looking across participants. (B) Difference in posterior probability of target looking between *related* and *unrelated* trials. The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
tibble::lst(data_time_related,
			data_time_related_oxf,
			data_time_related_vtarget,
			data_time_related_vtarget_oxf,
			data_time_related_vnone,
			data_time_related_vnone_oxf,
			data_time_related_noeach,
			data_time_related_noeach_oxf,
			data_time_related_vnoeach,
			data_time_related_vnoeach_oxf) |> 
	bind_rows(.id = "analysis") |>
	mutate(analysis_lab = case_when(
		analysis=="data_time_related" ~ "Analysis 1",
		grepl("_vtarget", analysis) ~ "Analysis 2",
		grepl("_vnone", analysis) ~ "Analysis 3",
		grepl("_noeach", analysis) ~ "Analysis 4",
		grepl("_vnoeach", analysis) ~ "Analysis 5",
		.default = "Analysis 1"
	),
	lp = ifelse(grepl("_oxf", analysis), 
				"Monolingual (English)", 
				as.character(lp)),
	lp = factor(lp, levels = c("Monolingual (English)",
							   "Monolingual",
							   "Bilingual"))) |> 
	# summarise(.elog_mean = mean(.elog),
	# 		  n = n(),
	# 		  .elog_std = sd(.elog),
	# 		  .by = c(condition, timebin, analysis, lp)) |>
	# mutate(.elog_se = .elog_std/n) |> 
	ggplot(aes(timebin, .elog,
			   colour = condition,
			   fill = condition,
			   shape = condition)) +
	facet_grid(analysis_lab~lp) +
	geom_hline(yintercept = 0.5, 
			   linewidth = 1/2,
			   colour = "black",
			   linetype = "dotted") +
	geom_smooth(method = lm, 
				se = FALSE, 
				formula = y ~ splines::bs(x, 4)) +
	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
	# 				  ymax = .elog_mean + .elog_se*1.96),
	# 			  width = 0.25,
	# 			  linewidth = 3/4) + 
	# geom_line(size = 3/4) + 
	stat_summary(fun = mean, geom = "point") +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 width = 0.25) +
	labs(x = "Time (ms)",
		 y = "P(Target looking)",
		 colour = "Condition",
		 fill = "Condition",
		 linetype = "Condition",
		 shape = "Condition") +
	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
	# scale_shape_manual(values = c(1, 2)) +
	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
											big.mark = ",")) +
	theme(legend.title = element_blank(),
		  axis.title.x = element_blank(),
		  panel.border = element_rect(fill = NA),
		  axis.line = element_line(),
		  legend.position = "top") 
```

```{r fig-cognate-summary}
#| label: fig-cognate-summary
#| fig-height: 6.5
#| fig-width: 8
#| fig-cap: "Marginal posterior predictions of the GAMMs. (A) Mean posterior probability of target looking across the time course of the trial. Black lines and intervals indicate the psoterior mean and 95% credible intervals. Points indicate the mean probability of target looking across participants. (B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials. The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
tibble::lst(data_time_cognate,
			data_time_cognate_oxf,
			data_time_cognate_vtarget,
			data_time_cognate_vtarget_oxf,
			data_time_cognate_vnone,
			data_time_cognate_vnone_oxf,
			data_time_cognate_noeach,
			data_time_cognate_noeach_oxf,
			data_time_cognate_vnoeach,
			data_time_cognate_vnoeach_oxf) |> 
	bind_rows(.id = "analysis") |>
	mutate(analysis_lab = case_when(
		analysis=="data_time_cognate" ~ "Analysis 1",
		grepl("_vtarget", analysis) ~ "Analysis 2",
		grepl("_vnone", analysis) ~ "Analysis 3",
		grepl("_noeach", analysis) ~ "Analysis 4",
		grepl("_vnoeach", analysis) ~ "Analysis 5",
		.default = "Analysis 1"
	),
	lp = ifelse(grepl("_oxf", analysis), 
				"Monolingual (English)", 
				as.character(lp)),
	lp = factor(lp, levels = c("Monolingual (English)",
							   "Monolingual",
							   "Bilingual"))) |> 
	# summarise(.elog_mean = mean(.elog),
	# 		  n = n(),
	# 		  .elog_std = sd(.elog),
	# 		  .by = c(condition, timebin, analysis, lp)) |>
	# mutate(.elog_se = .elog_std/n) |> 
	ggplot(aes(timebin, .elog,
			   colour = condition,
			   fill = condition,
			   shape = condition)) +
	facet_grid(analysis_lab~lp) +
	geom_hline(yintercept = 0.5, 
			   linewidth = 1/2,
			   colour = "black",
			   linetype = "dotted") +
	geom_smooth(method = lm, 
				se = FALSE, 
				formula = y ~ splines::bs(x, 4)) +
	# geom_errorbar(aes(ymin = .elog_mean - .elog_se*1.96, 
	# 				  ymax = .elog_mean + .elog_se*1.96),
	# 			  width = 0.25,
	# 			  linewidth = 3/4) + 
	# geom_line(size = 3/4) + 
	stat_summary(fun = mean, geom = "point") +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 width = 0.25) +
	labs(x = "Time (ms)",
		 y = "P(Target looking)",
		 colour = "Condition",
		 fill = "Condition",
		 linetype = "Condition",
		 shape = "Condition") +
	scale_linetype_manual(values = rev(c("solid", "dashed"))) +
	# scale_shape_manual(values = c(1, 2)) +
	scale_x_continuous(labels = \(x) format((x * 1e2)+300, 
											big.mark = ",")) +
	theme(legend.title = element_blank(),
		  axis.title.x = element_blank(),
		  panel.border = element_rect(fill = NA),
		  axis.line = element_line(),
		  legend.position = "top")
```

@@

```{r tbl-attrition-trials}
#| label: tbl-attrition-trials
#| tbl-cap: "Trial attrition rate by condition for included participants. Additional excluded trials are indicated between parentheses."
attrition_trials |> 
	filter(id %in% attrition_participants$id[attrition_participants$is_valid_participant]) |> 
	left_join(select(participants, filename, id, age_group),
			  by = join_by(filename, id, age_group)) |> 
	summarise(n_valid = sum(is_valid_trial),
			  n_total = n(),
			  .by = c(id, age_group, trial_type)) |> 
	summarise(across(n_valid, lst(sum, mean, sd),
					 .names = "{.fn}"),
			  n_total = sum(n_total),
			  .by = c(age_group, trial_type)) |> 
	mutate(n_excluded = n_total-sum) |> 
	select(-c(n_total)) |> 
	pivot_wider(names_from = trial_type,
				values_from = c(sum:sd, n_excluded),
				names_repair = janitor::make_clean_names) |> 
	rename_with(\(x) gsub("non_cognate", 
						  "noncognate",
						  x)) |> 
	arrange(age_group) |> 
	relocate(age_group,
			 matches("_cognate"),
			 matches("noncognate")) |> 
	gt(rowname_col = "age_group") |> 
	grand_summary_rows(columns = matches("mean_"),
					   fns = lst(Mean ~ mean(.)),
					   fmt = ~fmt_number(.)) |>
	grand_summary_rows(columns = matches("sum_"),
					   fns = lst(Sum ~ sum(.)),
					   fmt = ~fmt_integer(.)) |>
	cols_merge(c(sum_cognate, n_excluded_cognate), 
			   pattern = "{1} ({2})") |> 
	cols_merge(c(sum_noncognate, n_excluded_noncognate), 
			   pattern = "{1} ({2})") |> 
	cols_merge(c(sum_unrelated, n_excluded_unrelated),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(mean_cognate, sd_cognate),
			   pattern = "{1} ({2})") |>
	cols_merge(c(mean_noncognate, sd_noncognate),
			   pattern = "{1} ({2})") |>
	cols_merge(c(mean_unrelated, sd_unrelated),
			   pattern = "{1} ({2})") |>
	tab_spanner("Cognate trials", ends_with("_cognate")) |>
	tab_spanner("Non-cognate trials", ends_with("noncognate")) |> 
	tab_spanner("Unrelated trials", ends_with("unrelated")) |> 
	tab_spanner("Related trials", matches("cognate")) |>
	fmt_number(matches("mean|sd"), decimals = 1) |> 
	fmt_integer(matches("sum"), sep_mark = ",") |> 
	cols_label(sum_cognate = "N",
			   sum_noncognate = "N",
			   sum_unrelated = "N",
			   mean_cognate = "Mean",
			   mean_noncognate = "Mean",
			   mean_unrelated = "Mean")
```

@@

<!--
-->

```{r fig-related}
#| label: fig-related
#| fig-height: 6
#| fig-width: 8
#| fig-cap: "Marginal posterior predictions of the GAMMs. (A) Mean posterior probability of target looking across the time course of the trial. Black lines and intervals indicate the psoterior mean and 95% credible intervals. Points indicate the mean probability of target looking across participants. (B) Difference in posterior probability of target looking between *related* and *unrelated* trials. The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
epreds <- expand_grid(condition = levels(data_time_related$condition),
					  timebin = seq(0, 17, length.out = 100),
					  age = mean(data_time_related$age),
					  lp = levels(data_time_related$lp),
					  .nsamples = 1) |>
	add_epred_draws(model_fits_related[[1]],
					ndraws = NULL,
					re_formula = NA, 
					value = ".value") |> 
	mutate(lp = factor(lp, levels = c("Monolingual", "Bilingual")))

@@

## Analysis 5

Participants need to know the prime or target words, and do not need to look to both pictures.
